---
title: "MMSS 311-2 HW0"
author: "Yushi Liu"
date: "4/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
packages <- c("dplyr", "ggplot2", "lubridate", "stringr", "foreign")
load.packages <- function(x) {
  if (!require(x, character.only = TRUE)) {
    # character.only = TRUE specifies that the argument being passed to the function is in character type
    install.packages(x, dependencies = TRUE)
    # setting dependencies to TRUE will also install other packages that are necessary
    library(x, character.only = TRUE) # load the package once it has been installed
  }
}
lapply(packages, load.packages)
```

## Problem 1
(a) A vector with the numbers 1–5 in order

```{r}
v <- c(1:5)
v
```
(b) A scalar named Mindy that takes the value 12
```{r}
Mindy <- 12
Mindy
```
(c) A 2 × 3 matrix with the numbers 1–6 in order by rows
```{r}
byrow <- matrix(1:6, nrow = 2, ncol = 3, byrow = TRUE)
byrow
```
(d)
```{r}
bycol <- matrix(1:6, nrow = 2, ncol = 3)
bycol
```
(e)
```{r}
ones <- matrix(1, nrow = 10, ncol = 10)
```
(f)
```{r}
str <- c("THIS", "IS", "A", "VECTOR")

```
(g)
```{r}
sum3 <- function(a, b, c){
  return(a+b+c)
  print(a+b+c)
}
```
(h)
```{r}
YON <- function(n){
  if(n <= 10){
    return('Yes')
  }
  return('No')
}
```
(i)
```{r}
g <- rnorm(1000, mean = 10, sd = 1)

```
(j)
```{r}
y <- rnorm(1000, mean = 5, sd = 0.5)

```
(k) 
```{r}
x <- NULL
for (i in 1:1000){
  x[i] <- mean(sample(g, 10, replace = TRUE))
}
```
(j)
```{r}
lm <- lm(y ~ x)
summary(lm)
```
The coefficient is 0.03 but the p-value is not less than 0.05, so y doesn't have a significant increasing trend against x. 

## Problem 2
```{r}
setwd("~/Documents/GitHub/MMSS-311-2")
pums <- read.csv("pums_chicago.csv")
dim(pums)
```
(b) There are 204 variables and 50000 observations.
(c) See below
```{r}
annual_income <- mean(pums$PINCP, na.rm = TRUE)
```
(d)
```{r}
pums$PINCP_LOG <- log(pums$PINCP)
```
NaNs produced because some of the rows for annual incomes are NaNs. 
(e)
```{r}
pums$GRAD.DUMMY <- ifelse(pums$SCHL >= 18, "grad","not grad")
```
(f)
```{r}
df = subset(pums, select = -c(SERIALNO))
```
(g)
```{r}
write.csv(df, file = 'newdata.csv')
```
(h)
```{r}
under16 = pums[is.na(pums$ESR) == TRUE,]
pums_drop = pums[is.na(pums$ESR) == FALSE,]
employed = pums_drop[pums_drop$ESR == 1 | pums_drop$ESR == 2 , ]
unemployed = pums_drop[pums_drop$ESR == 3,]
armforce = pums_drop[pums_drop$ESR == 4 | pums_drop$ESR == 5 ,]
notinl = pums_drop[pums_drop$ESR == 6,]

```
Note that the "employed" category excludes the employed in armed forces. In words, "employed" dataframe only includes civilian employed. 
<br>
(i)
```{r}
new_frame = pums_drop[pums_drop$ESR == 1 | pums_drop$ESR == 2 | pums_drop$ESR == 4 | pums_drop$ESR == 5, ]
```
(j)
```{r}
library(dplyr)
employed_af = select(pums, c(AGEP, RAC1P, PINCP_LOG))
```
(k)-(i) First dropped all entries containing "NA".
```{r}
travelt = pums[is.na(pums$JWMNP) == FALSE,]$JWMNP
mean(travelt)
quantile(travelt, c(0.5, 0.8))


```
(k)-(ii)
```{r}
cor(pums$JWMNP, pums$WAGP, use = "complete.obs")
```
(k)-(iii) (iv)Scatterplot of age and log income
```{r}
pdf("graph for hw0.pdf")
plot(x=pums$AGEP, y=pums$PINCP_LOG)
dev.off()
```
(k)-(v) crosstab of ESR by race RAC1P
```{r}
cst <- table(pums$ESR, pums$RAC1P)
cst
```

(k)-(vi) Lienar regression of WAGP on WKHP
```{r}
lm1 <- lm(WAGP ~ WKHP, data = pums_drop)
summary(lm1)
```

(k)-(vii) Plot residuals from this regression against the fitted values
```{r}
plot(lm1$fitted.values,lm1$residuals)
```
The residual plot shows that there exists a linear relationship between residuals and fitted values. 

(l)-(i) A linear regression of miles per gallon (mpg) on weight (wt)
```{r}
mc <- mtcars
colnames(mtcars)
lm2 <- lm(mtcars$mpg~mtcars$wt)
summary(lm2)
```
(l)-(ii) First run the regression of mpg on wt for automatic transition cars. 
```{r}
at <- mtcars[mtcars$am == 0,]
m <- mtcars[mtcars$am == 1,]
lm3 <- lm(at$mpg~at$wt)
summary(lm3)
```
Then, run the regression of mpg on wt for manual cars.
```{r}
lm4 <- lm(m$mpg~m$wt)
summary(lm4)
```

(l)-(iii)
```{r}
lm5 <- lm(mtcars$mpg ~ log(mtcars$hp))
summary(lm5)
```
(m)-(i)
```{r}
mi <- ggplot(mtcars, aes(x=mpg, y=wt)) + geom_point()
show(mi)
```

(m)-(ii)
```{r}
ggplot(mtcars, aes(mpg, wt, color = am)) + geom_point()
```

(m)-(iii)
```{r}
ggplot(mtcars, aes(mpg, wt, color = am, size = gear)) + geom_point()
```

(m)-(iv)
```{r}
ggplot(mtcars, aes(mpg, wt, color = am, size = gear)) + geom_point() + labs(x = "Miles per gallon", y = "Weight")
```
(m) - (v)
```{r}
ggplot(mtcars, aes(mpg, wt, color = am, size = gear)) + geom_point() + labs(x = "Miles per gallon", y = "Weight") + theme(panel.background = element_rect(fill = "lightyellow"))
```

