---
title: "MMSS 311-2 HW0"
author: "Yushi Liu"
date: "4/12/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1
(a) A vector with the numbers 1–5 in order

```{r}
v <- c(1:5)
v
```
(b) A scalar named Mindy that takes the value 12
```{r}
Mindy <- 12
Mindy
```
(c) A 2 × 3 matrix with the numbers 1–6 in order by rows
```{r}
byrow <- matrix(1:6, nrow = 2, ncol = 3, byrow = TRUE)
byrow
```
(d)
```{r}
bycol <- matrix(1:6, nrow = 2, ncol = 3)
bycol
```
(e)
```{r}
ones <- matrix(1, nrow = 10, ncol = 10)
```
(f)
```{r}
str <- c("THIS", "IS", "A", "VECTOR")

```
(g)
```{r}
sum3 <- function(a, b, c){
  return(a+b+c)
  print(a+b+c)
}
```
(h)
```{r}
YON <- function(n){
  if(n <= 10){
    return('Yes')
  }
  return('No')
}
```
(i)
```{r}
g <- rnorm(1000, mean = 10, sd = 1)

```
(j)
```{r}
y <- rnorm(1000, mean = 5, sd = 0.5)

```
(k) 
```{r}
x <- NULL
for (i in 1:1000){
  x[i] <- mean(sample(g, 10, replace = TRUE))
}
```
(j)
```{r}
lm <- lm(y ~ x)
summary(lm)
```
The coefficient is 0.03 but the p-value is not less than 0.05, so y doesn't have a significant increasing trend against x. 

## Problem 2
```{r}
setwd("~/Documents/GitHub/MMSS-311-2")
pums <- read.csv("pums_chicago.csv")
dim(pums)
```
(b) There are 204 variables and 50000 observations.
(c) See below
```{r}
annual_income <- mean(pums$PINCP, na.rm = TRUE)
```
(d)
```{r}
pums$PINCP_LOG <- log(pums$PINCP)
```
NaNs produced because some of the rows for annual incomes are NaNs. 
(e)
```{r}
pums$GRAD.DUMMY <- ifelse(pums$SCHL >= 18, "grad","not grad")
```



